Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-02-20 automatica/paper.tex
+ comment

  % Additions from CAV:
  % continuous time
  % response time
  % floating point ?
\item We automatically generate {\em correct-by-construction} digital
  controllers using an inductive synthesis approach.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as quantizers and FWL.  %% In particular, we
  %% have found that a two-stage verification engine that continuously refines
  %% the precision of the fixed-point representation of the plant yields a
  %% speed-up of two orders of magnitude over a conventional one-stage
  %% verification engine.
%
  %\item  We compute
  The computed state-feedback controllers 
  guarantee a given safety property alongside stability and response time
  specifications.  Existing methods for controller synthesis rely on transfer
  function representations, which are inadequate to prove safety requirements.
%
\item We provide two novel algorithms: the first, na\"ive one, relies on
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant.
%
\item We develop a model for different sources of quantization error and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
\end{enumerate}

>>>>

  % Additions from CAV:
  % continuous time
  % response time ?
  % floating point 
\item We automatically generate {\em correct-by-construction} digital
  controllers using an inductive synthesis approach.  Our application of program
  synthesis is non-trivial and addresses challenges specific to control
  systems, such as quantizers and FWL.  %% In particular, we
  %% have found that a two-stage verification engine that continuously refines
  %% the precision of the fixed-point representation of the plant yields a
  %% speed-up of two orders of magnitude over a conventional one-stage
  %% verification engine.
%
  %\item  We compute
  The computed state-feedback controllers 
  guarantee a given safety property alongside stability and response time
  specifications \addtodo{CD: Do we actually consider response time in this paper?}.
  Existing methods for controller synthesis rely on transfer
  function representations, which are inadequate to prove safety requirements.
%
\item We provide two novel algorithms: the first, na\"ive one, relies on
  an unfolding of the dynamics up to a completeness threshold, while the
  second one is abstraction-based and leverages abstraction refinement and
  acceleration to improve scalability while retaining soundness.  %% A third
  %% algorithm evaluates systems using transfer functions where no state-space
  %% description is given.
  Both approaches provide sound synthesis of
  feedback controllers and consider the various sources of imprecision in
  the implementation of the control algorithm and in the modeling of the
  plant.
%
\item We develop a model for different sources of quantization error and
  their effect on reachability properties.  We give bounds that ensure the
  safety of our controllers in a hybrid continuous-digital domain.
\end{enumerate}
